### 2022-05-20 supplement.Rmd
Include sign of F for gender

# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
res_freq_2_lvl %>%
  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 0.30, 1.00)) ->
res_selection_weights

>>>>

# Easy weight function selection model (see metafor docs and Lauer et al., 2019)
res_freq_2_lvl %>%
  map(selmodel, type = "stepfun", steps = c(0.01, 0.05, 1.00)) ->
res_selection_weights
